---
title: "Two-stage Sampling Design Optimization with R2BEAT"
author: "Michael Wild and Giulio Barcaroli"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
              storyboard: true
              social: menu
              source_code: embed
              theme: spacelab
---

 

```{r setup, include=FALSE}
## options
options(future.globals.maxSize=10000*1024^2)
options(java.parameters = "- Xmx5g")
options(shiny.maxRequestSize=6000*1024^2)
## styles
smTab<-list(dom="tp")

```

```{css}
.sbframe-commentary .flexfill-container {
  width: 500px important!;
}
```

Column {.sidebar data-width=300}
-----------------------------------------------------------------------



```{r}
radioButtons("methodselect", "Select Approach", choices = c("R2BEAT"=1), selected = 1, inline = T)
## 1. Design Upload
h3("Design object")
h5("Only .RData!")
helpText("This is the result of the use",br(),
         "of ReGenesees function 'svydesign' ", br(),
         "applied to a previous round of the survey.")
loadFileInput(id = "desList",label = "Upload Design Data", accept = (c(".RData")))
des <<- callModule(loadFile, "desList")

## 2. Calibrated Upload
h3("Calibrated object")
h5("Only .RData!")
helpText("This is the result of the use",br(),
         "of ReGenesees function 'svycal' ", br(),
         "applied to a previous round of the survey.", br(),
         "N.B.: if the calibrated object does not exist,", br(),
         "      then reload the design object.")
loadFileInput(id = "calFile",label = "Upload Calibrated Data", accept = (c(".RData")))
cal <- callModule(loadFile, "calFile")

## 3. Primary Stage Units
h3("Primary Stage Units (PSUs)")
h5("Only .csv!")
helpText("In this dataset is contained ",br(),
         "all needed information related", br(),
         "to PSUs.")
zipFileInput(id = "psu",label = "Upload PSU dataset", accept = (c("text/csv", ".csv")))
psu<-callModule(zipFile, "psu")


h3("Parameters selection")

R2BEATInput(id = "updateStratInputs")

numericInput("delta", "Average number of final units for each selection unit", value = 1, min=0, step = 1)

numericInput("minimum", "Minimum number of SSUs to be selected in each PSU", value = 50, min=0, step = 1)

numericInput("seed", "Set Seed",value = floor(runif(1, 1000,9999)), min=0, step = 1)

```



### Design and calibrated objects

```{r}
observe({
  DES<<-des()
  shiny::validate(need(DES, message = "Upload design object first!"))
  callModule(R2BEATOutput1, "updateStratInputs", dataset = DES)
})
div(DT::renderDataTable(
  {DES<<-des()
   DES<<-DES$variables
   DT::datatable(DES)
    },rownames=FALSE),
style = "font-size:70%")
```

### PSU dataset

```{r}
observe({
  PSU<<-psu()
  shiny::validate(need(PSU, message = "Upload .csv file first!"))
  callModule(R2BEATOutput2, "updateStratInputs", dataset = PSU)
})
div(DT::renderDataTable(
  {PSU<<-psu()
    },rownames=FALSE),
  style = "font-size:70%")

```

*** 


After loading the data, and selecting the proper variables, click the start button. This will initiate the sampling design process, and present the results under the Sampling Properties section.
<br>
<br>

```{r}
# startButtonUI("start_design")
conditionalPanel("input.methodselect==1",
                 R2BEATInput_para("hotinputs")
)
# 

str_all_inputs<-callModule(R2BEATOutput_para, "hotinputs",
       dataset = DES,
       domain_var = reactive(input$`updateStratInputs-domain_var`),
       target_var = reactive(input$`updateStratInputs-target_var`)
)

# ## 1.1 collect variables in observer listening to start design optimization
start_design<-reactiveVal(); 
id_PSU<-reactiveVal();
id_SSU<-reactiveVal();
domain_var<-reactiveVal(); 
target_var<-reactiveVal(); 
strat_var<-reactiveVal();
deff_var<-reactiveVal();
frame_CV_in<<-reactiveVal();
PSU_id<<-reactiveVal();
stratum_var<-reactiveVal();
mos_var<-reactiveVal();
delta<-reactiveVal();
minimum<-reactiveVal();
seed<-reactiveVal();

# ## 1.2. run the observer w. reactive vals
observeEvent(input$`hotinputs-start_design`, {
  start_design(input$`hotinputs-start_design`)
  id_PSU(input$`updateStratInputs-id_PSU`)
  id_SSU(input$`updateStratInputs-id_SSU`)
  domain_var(input$`updateStratInputs-domain_var`)
  target_var(input$`updateStratInputs-target_var`)
  strat_var(input$`updateStratInputs-strat_var`)
  deff_var(input$`updateStratInputs-deff_var`)
  frame_CV_in(str_all_inputs$frame_CV_in())
  PSU_id(input$`updateStratInputs-PSU_id`)
  stratum_var(input$`updateStratInputs-stratum_var`)
  mos_var(input$`updateStratInputs-mos_var`)
  delta(input$delta)
  minimum(input$minimum)
  seed(input$seed)
})

observe({
  frame_CV <<- frame_CV_in()
  PSU_id <<- PSU_id
  stratum_var <<- stratum_var
  mos_var <<- mos_var
  delta <<- delta
  minimum <<- minimum
  seed <<- seed
})
# 
# 
# ## 3. Run optimal design

finalSample<<-callModule(R2BEATSRV, "start_design",
                        dataset1 = des(),
                        dataset2 = cal(),
                        dataset3 = psu(),
                        frame_CV_in = frame_CV,
                        start_design = start_design,
                        id_PSU = id_PSU,
                        id_SSU = id_SSU,
                        domain_var = domain_var,
                        target_var = target_var,
                        strat_var = strat_var,
                        deff_var = deff_var,
                        PSU_id = PSU_id,
                        stratum_var = stratum_var,
                        mos_var = mos_var,
                        delta = delta,
                        minimum = minimum,
                        seed = seed
)

```



### Final Sample

```{r}
observe({
  tab1 <<- finalSample$strata()
  tab2 <<- finalSample$rho()
  tab3 <<- finalSample$effst()
  tab4 <<- finalSample$iterations()
  tab5 <<- finalSample$sensitivity()
  tab6 <<- finalSample$expected()
  tab <<- finalSample$allocation()
  # plot1 <<- finalSample$plot1()
  # plot2 <<- finalSample$plot2()
  
})


tagList(
    fluidRow(
      column(4,
        h4("Iterations", style = "text-align: center;"),
        div(DT::renderDataTable({
          tab4
        },rownames=FALSE),style = "font-size:70%")
      ),
      column(4,
             h4("Sensitivity", style = "text-align: center;"),
        div(DT::renderDataTable({
          tab5
        },rownames=FALSE),style = "font-size:70%")
        # output$plot1 <- renderImage({
        #     outfile <- tempfile(fileext='.png')
        #     png(outfile, width=400, height=200)
        #     des <- tab
        #     des <- des[1:(nrow(des)-1),]
        #     strat <- c(as.character(as.numeric(des$Domain[1:(nrow(des)-1)])),"Tot")
        #     barplot(t(des[1:(nrow(des)),2:3]), names=strat,
        #             col=c("darkblue","red"), las=2, xlab = "Stratum", cex.axis=0.7, cex.names=0.7)
        #     legend("topleft", 
        #             legend = c("Self Representative","Non Self Representative"),
        #             fill = c("darkblue", "red"))
        #     title("Distribution of allocated PSUs by domain")
        #     dev.off()
        #     list(src = outfile,
        #          alt = "Plot1")
        #     }, deleteFile = TRUE),
        # plotOutput("plot1")
      ),
      column(4,
             h4("Expected CVs", style = "text-align: center;"),
        div(DT::renderDataTable({
          tab6
        },rownames=FALSE),style = "font-size:70%"),
      )
    )
  )


# DT::renderDataTable({
#   # if(isolate(input$methodselect)==1){
#   tab
#   # } 
# })
```


### Download Sample

```{r}
observe({
  tab <<- finalSample$sample()
  tab <<- tab[,c("Pik","STRATUM","PSU_ID","PSU_final_sample_unit","sampling_fraction","SR","nSR")]
})
div(DT::renderDataTable(
  tab,rownames=FALSE)
  ,style = "font-size:70%")
```

*** 

If you are satisfied with the current solution, click the button and start the download.
<br>
<br>

```{r}
conditionalPanel("input.methodselect==1",
                 downloadBigUI("dwl_sample", label = "Download Sample"))

observe({
    strata <- finalSample$strata()
    rho <- finalSample$rho()
    effst <- finalSample$effst()
    iterations <- finalSample$iterations()
    sensitivity <- finalSample$sensitivity()
    expected <- finalSample$expected()
    design <- finalSample$allocation()
    sample <- finalSample$sample()
    callModule(downloadBig, "dwl_sample", modid = "dwl_sample",
               strata = strata,
               rho = rho,
               effst = effst,
               iterations = iterations,
               sensitivity = sensitivity,
               expected = expected,
               design = design,
               sample = sample,
               seed = reactive(input$sampSEED)
               )
  })


```


***


